\documentclass[a4paper]{article}

\begin{document}

SNAKE\newline
\newline
A description of the game:\newline
The player controls a snake that moves forward continuously.
The player changes the direction of the snake by using the arrows. The goal of the game is to collect "apples" that appear on the playing field.
The player must avoid hitting the walls of the playing field. After "eating" the next "apple", the length of the snake increases by one.
The player wins when the snake reaches the maximum size (200 "pixels"). If the snake hits a boundary of the playing field, the player loses.\newline

The game has the following states:\newline
- Start — the state in which the game waits for the player to press the game ready button\newline
- Spawn apple — the state the game enters when an apple is eaten and the next apple's random place to spawn is selected\newline
- Moving - snake moves forward when timer's out\newline
- Acceleretion — snake moves forward, if a player choose an arrow like current direction of the snake\newline
- Turn — change direction of the snake to right/left of it's current direction\newline
- Eating apple and growing — if the snake touches an apple, it dissapears and the snake increases it's length by one\newline
- Pause — stops the game until Pause key is pressed\newline
- End — transition to the "Game Over" state\newline
- Victory — the state the game enters if current score reaches 200 points\newline
- Game over - option to restart or exit the game\newline
- Restart - go to start\newline
- Exit - close the program\newline
\newline
Points are awarded: 1 point for one apple\newline
The maximum score changes during the game,
if the user exceeds the current maximum score.
The maximum score is stored in a text file "snake\_score.txt" and is saved between program runs. 

Every time the player scores 5 points, the level increases by 1.
Increasing the level increases the speed of the snake. The maximum number of levels is 10.\newline

Information about the score, the maximum score and the current level are transmitted and displayed by the user interface in the sidebar.
\newline
\newline

TETRIS\newline
\newline
A description of the game:\newline
Tetris is probably one of the most popular games for the Brickgame console.
The console itself is often called Tetris. The goal of the game is to score points by building lines of blocks generated by the game.
The next block generated by the game begins to descend down the playing field until it reaches the bottom or collides with another block.
The user can rotate the figures and move them horizontally, trying to make rows.
After filling, the row is destroyed, the player receives points, and the blocks located above the filled row fall down.
The game ends when the next figure stops in the top row.
\newline

The game has the following states:\newline
- Start — the state in which the game waits for the player to press the game ready button.\newline
- Spawn — the state the game enters when the next block is created and the next block to spawn is selected.\newline
- Shift — moves blocks horizontally.\newline
- Rotate — rotates blocks.\newline
- Fall — the state the game enters after the timer expires. In this state, the current block moves down one level.\newline
- Pause — stops the game until Pause key is pressed.\newline
- End — transition to the "Game Over" state.\newline
- Connect — the state the game enters after the current block "touches" already fallen blocks or the ground.\newline
If filled lines are formed, they are destroyed and remaining blocks are shifted down.\newline
If the block stops in the top row, the game enters the "game over" state.\newline
- Game over - option to restart or exit the game.\newline
- Restart - go to start.\newline
- Exit the game - close the program.\newline

Points are awarded as follows:\newline
1 line - 100 points;\newline
2 lines - 300 points;\newline
3 lines - 700 points;\newline
4 lines - 1500 points.\newline

The maximum score changes during the game,
if the user exceeds the current maximum score.
The maximum score is stored in a text file "tetris\_score.txt" and is saved between program runs.
\newline
Every time the player scores 600 points, the level increases by 1.
Increasing the level increases the speed of the pieces. The maximum number of levels is 10.
\newline
\newline

CONTROL BUTTONS\newline
\newline
Control buttons for Qt games:\newline
- Start the game - 'S';\newline
- Pause - 'P';\newline
- End the game - 'Esc';\newline
- Turn or accelerate - Arrows;\newline
- Action - 'Space';\newline
- Restart - 'S' after the end of the game;\newline
- Exit - closing the game window.\newline
\newline

Control buttons for console games:\newline
- Start the game - any key;\newline
- Pause - 'P';\newline
- End the game - 'Q';\newline
- Turn or accelerate - Arrows;\newline
- Action - 'Space';\newline
- Restart - 'R' after the end of the game;\newline
- Exit - 'Q' after game over or victory.
\end{document}
